
# IMPORT

```{r}

library(tidyverse)
library(janitor)
library(lubridate)
library(readxl)

grouper <- function(input_df, group_by_column, new_column_name = "n()"){
  output_df <- input_df %>%
    group_by(.data[[group_by_column]]) %>%
    summarise(temp_count = n()) %>%
    mutate(percent = temp_count/sum(temp_count)*100) %>%
    arrange(desc(percent)) %>%
    rename(!!new_column_name := temp_count)
  return(output_df)
}

group_count <- function(input_df, group_column_name='n()', state_filter=NA, start_col = 1){
  column_names <- colnames(input_df)
  if(!is.na(state_filter)){
    input_df <- input_df %>%
      filter(state == state_filter)
  }
  for (column in column_names[start_col:length(column_names)]){
    output <- grouper(input_df, column, group_column_name)
    print(output)
  }
}

round_df <- function(x, digits) {
    # round all numeric variables
    # x: data frame 
    # digits: number of digits to round
    numeric_columns <- sapply(x, mode) == 'numeric'
    x[numeric_columns] <-  round(x[numeric_columns], digits)
    x
}

```

```{r}

#this code shows how the original was cleaned before unstructured text responses were classified

convert_column_to_logical <- function(input_df, column_name) {
  column_name <- enquo(column_name)
  
  output_df <- input_df %>%
    mutate({{ column_name }} := case_when(
      {{ column_name }} == "X" ~ TRUE,
      is.na({{ column_name }}) ~ FALSE
    ))
  
  return(output_df)
}

survey <- read_excel("data/permits_survey results.xlsx")

col_names <- paste(survey[1, ], survey[2, ], sep = "_")

col_names <- gsub("NA", "", col_names)

survey <- survey %>%
  set_names(col_names) %>%
  clean_names() %>%
  slice(3:nrow(survey)) %>%
  select(-submission_details_submitted_time) %>%
  rename(property_owner = are_you_a_property_owner_contractor_or_professional_permit_processor_property_owner) %>%
  convert_column_to_logical(property_owner) %>%
  convert_column_to_logical(contractor) %>%
  convert_column_to_logical(professional_permit_processor) %>%
  mutate(overall_experience_obtaining_a_permit = case_when(
    how_would_you_rate_your_overall_experience_obtaining_a_permit_from_the_city_of_baltimore_very_easy == "X" ~ "very easy",
    easy == "X" ~ "easy",
    somewhat_difficult == "X" ~ "somewhat difficult",
    difficult == "X" ~ "difficult",
    very_difficult == "X" ~ "very difficult"
  )) %>%
  select(-c(how_would_you_rate_your_overall_experience_obtaining_a_permit_from_the_city_of_baltimore_very_easy, easy, somewhat_difficult, difficult, very_difficult)) %>%
  relocate(property_owner, contractor, professional_permit_processor, overall_experience_obtaining_a_permit) %>%
  rename(use_permit = what_type_of_work_were_you_seeking_a_permit_to_perform_what_permit_service_did_you_apply_check_all_that_apply_use_permit) %>%
  convert_column_to_logical(use_permit) %>%
  convert_column_to_logical(demo_permit) %>%
  convert_column_to_logical(construction_permit_building_inspection) %>%
  convert_column_to_logical(construction_permit_construction) %>%
  convert_column_to_logical(construction_permit_encroachment_plan_planning) %>%
  convert_column_to_logical(construction_permit_encroachment_plan_fire) %>%
  convert_column_to_logical(construction_permit_permit_extensions) %>%
  convert_column_to_logical(construction_permit_demolition) %>%
  convert_column_to_logical(construction_permit_electrical) %>%
  convert_column_to_logical(construction_permit_gas_hvac) %>%
  mutate(were_you_aware_that_dhcd_provides_online_tutorials_and_training_session_on_the_permitting_process = case_when(
    were_you_aware_that_dhcd_provides_online_tutorials_and_training_session_on_the_permitting_process_yes == "X" ~ "yes",
    no == "X" ~ "no"
  )) %>%
  select(-c(were_you_aware_that_dhcd_provides_online_tutorials_and_training_session_on_the_permitting_process_yes, no)) %>%
  mutate(have_you_ever_utilized_an_of_the_online_tutorials_available_on_the_dhcd_website_to_assist_in_obtaining_your_permit = case_when(
    	have_you_ever_utilized_an_of_the_online_tutorials_available_on_the_dhcd_website_to_assist_in_obtaining_your_permit_yes == "X" ~ "yes",
    	no_2 == "X" ~ "no"
  )) %>%
  select(-c(have_you_ever_utilized_an_of_the_online_tutorials_available_on_the_dhcd_website_to_assist_in_obtaining_your_permit_yes, no_2
)) %>%
  unique() %>%
  mutate(row_id = row_number()) %>%
  relocate(row_id) 

```



```{r}

#this version includes manual classification by the baltimore banner
survey <- read_csv("data/clean-survey.csv")

```
# FACTCHECK

## "Not all reviews were negative, but nearly four out of every five respondents said the process was difficult."

```{r}

glimpse(survey)

t <- survey %>%
  mutate(difficult = case_when(
    str_detect(overall_experience_obtaining_a_permit, "difficult") ~ TRUE,
    TRUE ~ FALSE
  )) %>%
  group_by(difficult) %>%
  count()

t %>%
  mutate(perc = n/sum(t$n))

```

## "More than one in three said it was very difficult."

```{r}

grouper(survey, "overall_experience_obtaining_a_permit")

```

## "More than a third of survey respondents said it took longer than 60 days to get their permit approved or denied."

```{r}

grouper(survey, "approximately_how_long_did_it_take_from_the_time_you_applied_for_your_permit_to_receiving_an_approval_or_denial")

```

## "Getting encroachment plan permits — which authorize work on city and state-owned land — take the longest."

```{r}

use_permit <- survey %>%
  filter(use_permit == TRUE)

demo_permit <- survey %>%
  filter(demo_permit == TRUE)

construction_permit_building_inspection <- survey %>%
  filter(construction_permit_building_inspection == TRUE)

construction_permit_construction <- survey %>%
  filter(construction_permit_construction == TRUE)

construction_permit_encroachment_plan_fire <- survey %>%
  filter(construction_permit_encroachment_plan_fire == TRUE)

construction_permit_encroachment_plan_planning <- survey %>%
  filter(construction_permit_encroachment_plan_planning == TRUE)

construction_permit_permit_extensions <- survey %>%
  filter(construction_permit_permit_extensions == TRUE)

construction_permit_demolition <- survey %>%
  filter(construction_permit_demolition == TRUE)

construction_permit_electrical <- survey %>%
  filter(construction_permit_electrical == TRUE)

construction_permit_gas_hvac <- survey %>%
  filter(construction_permit_gas_hvac == TRUE)

calc_and_pivot_df <- function(party, group_by_column){
  
  input_df <- eval(parse(text = party))
  
  temp_input_df <- input_df %>%
    group_by(.data[[group_by_column]]) %>%
    count() %>%
    ungroup()

  raw_input_df <- temp_input_df %>%
    pivot_wider(values_from = n, names_from = .data[[group_by_column]]) %>%
    mutate(party = party,
           type = "raw") %>%
    relocate(party, type)
  
  perc_input_df <- temp_input_df  %>%
    mutate(percent = (n/sum(n))*100) %>%
    select(-n) %>%
    pivot_wider(values_from = percent, names_from = .data[[group_by_column]]) %>%
    mutate(party = party,
           type = "perc") %>%
    relocate(party, type)
  
  return(raw_input_df %>%
    bind_rows(perc_input_df) %>%
    clean_names())
  
}

analyze_column_by_permit <- function(group_by_column, digits=1) {
  
  #group_by_column <- "approximately_how_long_did_it_take_from_the_time_you_applied_for_your_permit_to_receiving_an_approval_or_denial"
  
  t1 <- calc_and_pivot_df("use_permit", group_by_column)
  t2 <- calc_and_pivot_df("demo_permit", group_by_column)
  t4 <- calc_and_pivot_df('construction_permit_building_inspection', group_by_column)
  t5 <- calc_and_pivot_df('construction_permit_construction', group_by_column)
  t6 <- calc_and_pivot_df('construction_permit_encroachment_plan_fire', group_by_column)
  t7 <- calc_and_pivot_df('construction_permit_encroachment_plan_planning', group_by_column)
  t8 <- calc_and_pivot_df('construction_permit_permit_extensions', group_by_column)
  t9 <- calc_and_pivot_df('construction_permit_demolition', group_by_column)
  t10 <- calc_and_pivot_df('construction_permit_electrical', group_by_column)
  t11 <- calc_and_pivot_df('construction_permit_gas_hvac', group_by_column)
  
  
  output <- t1 %>%
    bind_rows(t2, t4, t5, t6, t7, t8, t9, t10, t11)
  
  return(output %>%
           round_df(digits))
  
}

analyze_column_by_permit("approximately_how_long_did_it_take_from_the_time_you_applied_for_your_permit_to_receiving_an_approval_or_denial") %>%
  filter(type == "raw") %>%
  arrange(desc(greater_than_60_days))

```

## "About one-third of respondents specifically cited poor communication and long response times as the biggest challenges to getting permits."

```{r}

grouper(survey, "challenge_poor_communication_response_time")

```

## "More than 50 survey respondents said they had encountered “rude” city employees or received conflicting information."

```{r}

survey %>%
  filter(challenge_conflicting_info == TRUE) %>%
  bind_rows(survey %>%
              filter(challenge_rude_difficult_staff == TRUE)) %>%
  unique()

```